Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2016-05-02 manuscript-final.tex
Add tex file with bib inside

\pdfoutput=1
%\documentclass[paper,twocolumn,twoside]{geophysics}
%\documentclass[manuscript]{geophysics}
\documentclass[manuscript,endfloat]{geophysics}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\newcommand{\mitbf}[1]{\mathbf{{#1}}}

% To leave comments
\usepackage[colorinlistoftodos]{todonotes}

@@

\bibliographystyle{seg}
\bibliography{references.bib}
\end{document}

>>>>

\documentclass[manuscript,endfloat]{geophysics}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\newcommand{\mitbf}[1]{\mathbf{{#1}}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{}
\itemsep0pt

\bibitem[{\'A}lvarez et~al., 2012]{Alvarez2012}
{\'A}lvarez, O., M. Gimenez, C. Braitenberg, and A. Folguera,  2012, {GOCE}
  satellite derived gravity and gravity gradient corrected for topographic
  effect in the south central andes region: {GOCE} derivatives in the south
  central andes: Geophysical Journal International, {\bf 190}, 941--959.

\bibitem[Asgharzadeh et~al., 2007]{Asgharzadeh2007}
Asgharzadeh, M.~F., R.~R.~B. von Frese, H.~R. Kim, T.~E. Leftwich, and J.~W.
  Kim,  2007, Spherical prism gravity effects by {Gauss}-legendre quadrature
  integration: Geophysical Journal International, {\bf 169}, 1--11.

\bibitem[Barrera-Figueroa et~al., 2006]{Barrera-Figueroa2006}
Barrera-Figueroa, V., J. Sosa-Pedroza, and J. L{\'o}pez-Bonilla,  2006,
  Multiple root finder algorithm for legendre and {Chebyshev} polynomials via
  {Newton\textquoteright}s method: Annales Mathematicae et Informaticae,
  3{\textendash}13.

\bibitem[Bouman et~al., 2013a]{Bouman2013}
Bouman, J., J. Ebbing, and M. Fuchs,  2013a, Reference frame transformation of
  satellite gravity gradients and topographic mass reduction: Journal of
  Geophysical Research: Solid Earth, {\bf 118}, 759--774.

\bibitem[Bouman et~al., 2013b]{Bouman2013a}
Bouman, J., J. Ebbing, S. Meekes, R. Abdul~Fattah, M. Fuchs, S. Gradmann, R.
  Haagmans, V. Lieb, M. Schmidt, D. Dettmering, and W. Bosch,  2013b, {GOCE}
  gravity gradient data for lithospheric modeling: International Journal of
  Applied Earth Observation and Geoinformation, {\bf 35}, 16--30.

\bibitem[Braitenberg, 2015]{Braitenberg2015}
Braitenberg, C.,  2015, Exploration of tectonic structures with {GOCE} in
  {Africa} and across-continents: International Journal of Applied Earth
  Observation and Geoinformation, {\bf 35}, 88--95.

\bibitem[Braitenberg et~al., 2013]{Braitenberg2014}
Braitenberg, C., P. Mariani, and A. De~Min,  2013, The {Europe}an alps and
  nearby orogenic belts sensed by {GOCE}: Bollettino di Geofisica Teorica e
  Applicata, {\bf 54}, 321--334.

\bibitem[Braitenberg et~al., 2011]{Braitenberg2011}
Braitenberg, C., P. Mariani, J. Ebbing, and M. Sprlak,  2011, The enigmatic
  {Chad} lineament revisited with global gravity and gravity-gradient fields:
  Geological Society, London, Special Publications, {\bf 357}, 329--341.

\bibitem[Fullea et~al., 2014]{Fullea2014}
Fullea, J., J. Rodr{\'i}guez-Gonz{\'a}lez, M. Charco, Z. Martinec, A. Negredo,
  and A. Villase{\~n}or,  2014, Perturbing effects of sub-lithospheric mass
  anomalies in {GOCE} gravity gradient and other gravity data modelling:
  Application to the atlantic-mediterranean transition zone: International
  Journal of Applied Earth Observation and Geoinformation, {\bf 35}, 54--69.

\bibitem[Grombein et~al., 2013]{Grombein2013}
Grombein, T., K. Seitz, and B. Heck,  2013, Optimized formulas for the
  gravitational field of a tesseroid: Journal of Geodesy, {\bf 87}, 645--660.

\bibitem[Heck and Seitz, 2007]{Heck2007}
Heck, B., and K. Seitz,  2007, A comparison of the tesseroid, prism and
  point-mass approaches for mass reductions in gravity field modelling: Journal
  of Geodesy, {\bf 81}, 121--136.

\bibitem[Hildebrand, 1987]{Hildebrand1987}
Hildebrand, F.~B.,  1987, Introduction to numerical analysis: Dover
  Publications.

\bibitem[Hunter, 2007]{Hunter2007}
Hunter, J.~D.,  2007, Matplotlib: {A} 2d graphics environment: Computing in
  Science \& Engineering, {\bf 9}, 90--95.

\bibitem[Ku, 1977]{Ku1977}
Ku, C.~C.,  1977, A direct computation of gravity and magnetic anomalies caused
  by 2-and 3-dimensional bodies of arbitrary shape and arbitrary magnetic
  polarization by equivalent-point method and a simplified cubic spline:
  Geophysics, {\bf 42}, 610{\textendash}622.

\bibitem[{LaFehr}, 1991]{Lafehr1991}
{LaFehr}, T.,  1991, An exact solution for the gravity curvature ({Bullard}
  {B}) correction: {GEOPHYSICS}, {\bf 56}, 1179--1184.

\bibitem[Li et~al., 2011]{Li2011}
Li, Z., T. Hao, Y. Xu, and Y. Xu,  2011, An efficient and adaptive approach for
  modeling gravity effects in spherical coordinates: Journal of Applied
  Geophysics, {\bf 73}, 221--231.

\bibitem[Mariani et~al., 2013]{Mariani2013}
Mariani, P., C. Braitenberg, and N. Ussami,  2013, Explaining the thick crust
  in paran{\'a} basin, {Brazil}, with satellite {GOCE} gravity observations:
  Journal of South American Earth Sciences, {\bf 45}, 209--223.

\bibitem[McKinney, 2010]{Mckinney2010}
McKinney, W.,  2010, Data structures for statistical computing in python:
  Proceedings of the 9th Python in Science Conference, 51 -- 56.

\bibitem[Miku{\v s}ka et~al., 2006]{Mikuska2006}
Miku{\v s}ka, J., R. {Pa}{\v s}teka, and I. {Maru}{\v s}iak,  2006, Estimation
  of distant relief effect in gravimetry: {GEOPHYSICS}, {\bf 71}, J59--J69.

\bibitem[P\'erez and Granger, 2007]{Perez2007}
P\'erez, F., and B.~E. Granger,  2007, {IP}ython: a system for interactive
  scientific computing: Computing in Science and Engineering, {\bf 9}, 21--29.

\bibitem[Ramachandran and Varoquaux, 2011]{Ramachandran2011}
Ramachandran, P., and G. Varoquaux,  2011, Mayavi: 3d visualization of
  scientific data: Computing in Science \& Engineering, {\bf 13}, 40--51.

\bibitem[Reguzzoni et~al., 2013]{Reguzzoni2013}
Reguzzoni, M., D. Sampietro, and F. Sanso,  2013, Global {Moho} from the
  combination of the {CRUST}2.0 model and {GOCE} data: Geophysical Journal
  International, {\bf 195}, 222--237.

\bibitem[{Uieda}, 2015]{uieda2015}
{Uieda}, L.,  2015, A tesserioid (spherical prism) in a geocentric coordinate
  system with a local-{{North}}-oriented coordinate system: figshare, available
  from: http://dx.doi.org/10.6084/m9.figshare.1495525.
\newblock (Accessed May 2016).

\bibitem[Wild-Pfeiffer, 2008]{Wild-Pfeiffer2008}
Wild-Pfeiffer, F.,  2008, A comparison of different mass elements for use in
  gravity gradiometry: Journal of Geodesy, {\bf 82}, 637--653.

\end{thebibliography}

\end{document}
